My title

### 2024-03-09 paper/paper.qmd
new addition

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#|label: tbl-modelresults1
#| tbl-cap: ""Explanatory models Political Preferences (n = 1000)"

@@

modelsummary(
  list(
    "Support Biden" = political_preferences1
  ),
  statistic = "mad"
  )
```

```{r}
# Extract posterior samples
posterior_samples <- as.matrix(political_preferences)

# Calculate credible intervals (e.g., 95%)
credible_intervals <- apply(posterior_samples, 2, function(x) quantile(x, c(0.025, 0.975)))

# Extract coefficient names
coefficient_names <- colnames(posterior_samples)

# Create a data frame with coefficient names, coefficient estimates, and credible intervals
table_data <- data.frame(
  Posterior_Mean = colMeans(posterior_samples),
  Credible_Interval_Lower = credible_intervals[1, ],
  Credible_Interval_Upper = credible_intervals[2, ]
)

# Print the table
print(table_data)

@@

```{r}
modelplot(political_preferences1, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```
```{r}
# Create the model plot
model_plot <- modelplot(political_preferences1, conf_level = 0.9)

>>>>

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in

[Appendix -@sec-model-details].

@@

To avoid exessive runtime, we randomly sampled 1000 observations to fit the model.

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-modelresults1
#| tbl-cap: "Explanatory models Political Preferences (n = 1000)"

@@

# Change variable names directly in the model object
names(political_preferences1$coefficients) <- c(
  "Intercept", "Black", "Hispanic", "Middle Eastern", "Native American", 
  "Other race", "Two or more races", "White", "Northeast", "South", "West",
  "Homemaker", "Other employment", "Part-time", "Permanently disabled", 
  "Retired", "Student", "Temporarily laid off", "Unemployed"
)

modelsummary(
  list(
    "Support Biden" = political_preferences1
  ),
  statistic = "mad"
  )
```
# need to be fixed
Our results generally matches our justification. To avoid multicollinearity, the model excluded three variables from each category: race Asian, region Midwest, and employed full-time.

The intercept represents the estimated log-odds of supporting Biden when all other predictors are held constant at their reference levels. In this case, the estimated log-odds of supporting Biden for individuals who are Asian, live in the Midwest, and are employed full-time is 0.806.

Black people's support for Biden is large. The estimated coefficient of 2.549 means that, holding all other variables constant, Black individuals are estimated to have a 2.549 unit increase in the log-odds of supporting Biden compared to the reference group.

Hispanic races on average are also more likely to vote for Biden. (not significant)
We observe an outlier race other which has a 37.999 higher log-odds of supporting Biden compared to the reference group.

```{r}

# Define the updated variable names
new_coef_names <- c(
  "Intercept", "Black", "Hispanic", "Middle Eastern", "Native American", 
  "Other race", "Two or more races", "White", "Northeast", "South", "West",
  "Homemaker", "Other employment", "Part-time", "Permanently disabled", 
  "Retired", "Student", "Temporarily laid off", "Unemployed"
)

# Update variable names in the model object
names(political_preferences1$coefficients) <- new_coef_names

# Print the updated model summary
print(
  modelsummary(
    list("Support Biden" = political_preferences1),
    statistic = "mad"
  )
)

@@

```{r}

# Print the updated model summary with modified variable names
print(
  modelsummary(
    list("Support Biden" = political_preferences1),
    statistic = "mad",
    coef_map = list(
      Intercept = "Intercept",
      raceBlack = "Black",
      raceHispanic = "Hispanic",
      raceMiddle_Eastern = "Middle Eastern",
      raceNative_American = "Native American",
      raceOther = "Other race",
      `raceTwo or more races` = "Two or more races",
      raceWhite = "White",
      regionNortheast = "Northeast",
      regionSouth = "South",
      regionWest = "West",
      employHomemaker = "Homemaker",
      employOther = "Other employment",
      employPart_time = "Part-time",
      employPermanently_disabled = "Permanently disabled",
      employRetired = "Retired",
      employStudent = "Student",
      `employTemporarily laid off` = "Temporarily laid off",
      employUnemployed = "Unemployed"
    )
  )
)

```{r}
# Extract posterior samples
# posterior_samples <- as.matrix(political_preferences)
# 
# # Calculate credible intervals (e.g., 95%)
# credible_intervals <- apply(posterior_samples, 2, function(x) quantile(x, c(0.025, 0.975)))
# 
# # Extract coefficient names
# coefficient_names <- colnames(posterior_samples)
# 
# # Create a data frame with coefficient names, coefficient estimates, and credible intervals
# table_data <- data.frame(
#   Posterior_Mean = colMeans(posterior_samples),
#   Credible_Interval_Lower = credible_intervals[1, ],
#   Credible_Interval_Upper = credible_intervals[2, ]
# )
# 
# # Print the table
# print(table_data)

```
Due to the fact that the credibility interval for race Other is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables. That's why we created a second plot with the x axis limited from -10 to 10.

```{r}
modelplot(political_preferences1, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```

```{r}
# Create the model plot
model_plot <- modelplot(political_preferences1, conf_level = 0.9)
